Numerical Analysis \\ Assignment 9

### 2017-11-01 Graduate - Numerical Analysis/Assignment 10/assignment.tex
update

\problem{4}{Problem 4.23, Page 243}
\solution{Solution}{
We know the orthogonal functions on $[-1, 1]$ with weight function $w(x) = \frac{1}{\sqrt{1-x^2}}$ are Chebyshev polynomials:
$$
T_0(x) = 1, ~T_1(x) = x, ~T_2(x) = 2x^2-1.
$$
For any $p(x) = a_0+a_1x+a_2x^2 $ of degree 2 that minimizes the distance, we have
$$
a_j = (f, T_j), ~j = 0, 1, 2.
$$
Thus
$$
a_0 = (f, T_0) = \int_{-1}^{1} \frac{1}{\sqrt{1-x^2}}\cos^{-1}xdx = \int_{\pi}^{0}-ydy = \frac{\pi^2}{2},
$$
$$
a_1 = (f, T_1) = \int_{-1}^{1}\frac{x}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\int_{0}^{\pi} y\cos ydy = y\sin y\right|_{0}^{\pi} - \int_{0}^{\pi} \sin ydy = -2,
$$
$$
a_2 = (f, T_2) = \int_{-1}^{1}\frac{2x^2-1}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\int_{0}^{\pi}y\cos 2ydy = \frac{y\sin 2y}{2}\right|_{0}^{\pi} - \frac{1}{2}\int_{0}^{\pi}\sin 2ydy = -\frac{1}{2}.
$$
Thus
$$
p_2(x) = -\frac{1}{2}x^2-2x+\frac{\pi^2}{2}.
$$
}
\end{document}

>>>>

\problem{4}{Problem 4.23, Page 243}
\solution{Solution}{
We know the orthogonal functions on $[-1, 1]$ with weight function $w(x) = \frac{1}{\sqrt{1-x^2}}$ are Chebyshev polynomials (normalized):
$$
T_0(x) = \frac{1}{\sqrt{\pi}}, ~T_1(x) = \sqrt{\frac{2}{\pi}}x, ~T_2(x) = \sqrt{\frac{2}{\pi}}(2x^2-1).
$$
For any $p(x) = a_0+a_1x+a_2x^2 $ of degree 2 that minimizes the distance, we have
$$
a_j = (f, T_j), ~j = 0, 1, 2.
$$
Thus
$$
a_0 = (f, T_0) = \frac{1}{\sqrt{\pi}}\int_{-1}^{1} \frac{1}{\sqrt{1-x^2}}\cos^{-1}xdx = \frac{1}{\sqrt{\pi}}\int_{\pi}^{0}-ydy = \frac{(\pi)^{\frac{3}{2}}}{2},
$$
$$
a_1 = (f, T_1) = \sqrt{\frac{2}{\pi}}\int_{-1}^{1}\frac{x}{\sqrt{1-x^2}}\cos^{-1}xdx = \left.\sqrt{\frac{2}{\pi}}\int_{0}^{\pi} y\cos ydy = \sqrt{\frac{2}{\pi}}(y\sin y\right|_{0}^{\pi} - \int_{0}^{\pi} \sin ydy) = -\sqrt{\frac{8}{\pi}},
$$
$$
a_2 = (f, T_2) = \sqrt{\frac{2}{\pi}}\int_{-1}^{1}\frac{2x^2-1}{\sqrt{1-x^2}}\cos^{-1}xdx = \sqrt{\frac{2}{\pi}}\left.\int_{0}^{\pi}y\cos 2ydy = \sqrt{\frac{2}{\pi}}(\frac{y\sin 2y}{2}\right|_{0}^{\pi} - \frac{1}{2}\int_{0}^{\pi}\sin 2ydy) = 0,
$$
Thus
$$
p_2(x) = -\frac{4}{\pi}x+\frac{\pi}{2}.
$$
}
\end{document}
